---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# readme2pkg

<!-- badges: start -->
<!-- badges: end -->

The goal of readme2pkg collects strategies for making the README.Rmd the main workplace and/or storytelling document. 


0000. create repo github? coolest_pkg
000. create directory ("coolest_pkg) via projects, linking your repo
00. create README.rmd in a directory via usethis::use_readme_rmd()
0. Write problem statement (might be verbose code)
1. write useful code (might be rearrangement of verbose code into a function) 
2. test interactively
3. create package folder architecture, e.g. devtools::create("../coolest_pkg/")
3. send function to .R folder `readme2pkg::chunk_to_dir_r()`
4. formalize test and send to test folder `readme2pkg::chunk_to_dir_tests_testthat()`
5. iterate; run checks; build; document; push to github; tell your friends
6. move to 'later stage' (functions and tests 1st home is no longer README, but R and tests folders)
7. promote
    - refine readme language to publication ready
    - create publication source file .Rmd; pull in portion of readme as child
    - create other promo, pull in readme in a way that allow chunk quotation and reuse

# Origins

where this emerged?  

- ind2cat; ggjudge; mytidytuesday
- reflecting on litr - very similar framework, but too bundled up for me, greater focus on package development.

# Very early stage development, function development in the .RMD



# Write some functions



````{verbatim}

```{r one_plus_one}
one_plus_one <- function(){1 + 1}
```


```{r two_plus_two}
two_plus_two <- function(){2 + 2}
```

````


# try out the functions

these little tests might also serve as function examples - note that you can insert a roxygen skeleton within code chunks.

````{verbatim} 

```{r trying out the function}
one_plus_one()
two_plus_two()
```


````


# send function to .R

````{verbatim} 

```{r}
chunk_to_r(chunk_name = c("one_plus_one", 
                              "two_plus_two"))
```

````



## Formalized 'trying out function' as tests

````{verbatim}

```{r test_judge_chunk_code, eval = }
testthat::test_that("multiplication works", {
  expect_equal(two_plus_two(), 4)
})
```
````


## send function to tests/testthat file



````{verbatim} 

```{r, eval = F}
chunk_send_to_dir_tests_testthat("test_judge_chunk_code")
```

````


# Run checks w devtools, adjust code in Rmd as needed.  Install package, restart R.

# tell your friends about your work in progress; remotes::install_github()

# Awkward in-between phase Turn off function chunks and load library at top of .Rmarkdown; execute to make sure package itself is working?



# Later stage development

After the initial stage of development the homebase of functions should probably change to be true to the package structure.

Eventually things will feel circular and hairy if you do to much development in the .Rmd.  So, you will want the homebase of your code to be in the R folder and in a .R file.

You should delete the development code chunks.   (check the contents out of .R filse before making this move, lol. ) 

Then you can quote ".R" functions if would like to show the details of your implementation, as follows. 


````{verbatim}

```{r}
readLines("R/two_plus_two.R") -> implementation
```

```{r, code = implementation, eval= F}
```

````


# Time to promote your package 


For more summarized products, you might want to use your thoughtfully crafted examples 
from README.Rmd without all the readme text... 

Strategy from within an addition .Rmd file (slides, motivation letter)

````{verbatim}


```{r read_in_chunks, eval = F, echo = F, results='hide'}
knitr::knit_child("../../../README.rmd")
```

```{r}
knitr::knit_code$get() |> names() # lists all current doc chunk names including from child README.rmd
```

````



# Journal article

The Rmd itself may serve as the basis for a journal article.  Hopefully, the writing will just get better and better from the different vantage points.  

A strategy...


````{verbatim}

---
title: "Article Proposal: Concise indicator variable recoding with ind2cat"
author:
  # see ?rjournal_article for more information
  - name: Evangeline Reynolds
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
abstract: >
  Indicator variables are easy to create, store, and interpret....
bibliography: RJreferences.bib
output: rticles::rjournal_article
---




```{r, include=F}
knitr::opts_chunk$set(message = F, 
                      warning = F, 
                      comment = "    ", 
                      out.width = "69%")
kabel_format <- "latex"


library(magrittr)
readLines("../../../README.Rmd")  %>%  .[44:length(.)] %>% 
  writeLines("../../../readme_extract.Rmd")
```

```{r, child = "../../../readme_extract.Rmd"}
```



````
